\chapter[remote-control-regulatory-compliance-statements]{Remote Control Regulatory Compliance Statements}

\section[fcc-information]{FCC Information}

This device complies with Part 15 of the FCC Rules. Operation is subject to the following two conditions: (1) This device may not cause harmful interference, and (2) this device must accept any interference received, including interference that may cause undesired operation.

\startNOTE{Caution:}
Changes or modifications not expressly approved by Tessonics Inc. could void the user’s authority to operate this device.
\stopNOTE

\startNOTE{Note:}
This equipment has been tested and found to comply with the limits for a Class A digital device, pursuant to Part 15 of the FCC Rules. These limits are designed to provide reasonable protection against harmful interference when the equipment is operated in a commercial environment. This equipment generates, uses, and can radiate radio frequency energy and, if not installed and used in accordance with the instruction manual, may cause harmful interference to radio communications. Operation of this equipment in a residential area is likely to cause harmful interference in which case the user will be required to correct the interference at his own expense.
\stopNOTE

\section[industry-canada-information]{Industry Canada Information}

This Class A digital apparatus complies with Canadian ICES-003

Cet appareil numérique de la classe A est conforme à la norme NMB-003 du Canada

Operation is subject to the following two conditions: (1) this device may not cause interference, and (2) this device must accept any interference, including interference that may cause undesired operation of the device.

To reduce potential radio interference to other users, the antenna type and its gain should be so chosen that the equivalent isotropically radiated power (e.i.r.p.) is not more than that permitted for successful communication.

To prevent radio interference to the licensed service, this device is intended to be operated indoors and away from windows to provide maximum shielding. Equipment (or its transmit antenna) that is installed outdoors is subject to licensing.

The Term \quotation{IC:} before the certification/registration number only signifies that the Industry Canada technical specifications were met.

\section[european-community-compliance-information]{European Community Compliance Information}

\startWARNING{Warning:}
This is a Class A product. In a domestic environment this product may cause radio interference in which case the user may be required to take adequate measures.
\stopWARNING